Self Regulation Ontology Retest Data Report

### 2017-04-21 SRO_Report.Rmd
began changes based on meeting

```{r warning=FALSE, message=FALSE, fig.width=12}
measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
  select(measure_type, icc, spearman) %>%
  gather(key, value, -measure_type) %>%
  ggplot(aes(value, fill=key))+
  geom_histogram(position='identity', alpha=0.5)+
  theme_bw()+
  facet_wrap(~measure_type)+
  theme(legend.title = element_blank())
```

@@

tmp %>% ggplot(aes(value, color=label_2, fill=label_3))+
  geom_histogram(position='identity', alpha = 0.5)+
  theme_bw()+
  facet_wrap(key~label_1)+
  labs(color="Model", fill="Parameter")
```

>>>>

```{r warning=FALSE, message=FALSE, fig.width=12, fig.height=10}
measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  select(-measure_description, -notes, -variable_type, -task, -ddm_task) %>%
  left_join(icc_df[,c("dv", "icc")], by='dv') %>%
  left_join(cor_df[,c("dv", "spearman")], by='dv') %>%
  select(measure_type, icc, spearman) %>%
  gather(key, value, -measure_type) %>%
  ggplot(aes(value, fill=key))+
  geom_histogram(position='identity', alpha=0.5)+
  theme_bw()+
  facet_wrap(~measure_type)+
  theme(legend.title = element_blank())
```

@@

tmp %>% ggplot(aes(label_2, value, fill=label_3))+
  geom_boxplot()+
  theme_bw()+
  facet_wrap(key~label_1)+
  labs(fill="Parameter")
```
